Re-fit

### 2022-06-16 scripts/r/04_refit/refit_jvc.Rmd
testing after merge

directory <- here("osf", "data", "production", "trial-lists")
list_of_files = dir(here("osf", "data", "production", "trial-lists"))

@@

#
# JVC: ORIGINAL MODEL (singular fit)
#
intensity_model_lmer <- lmer(Intensity ~ typ_mean + (1|target_name)+ (1|filename) + (1|filename:target_name),
                       data = intensity_DF)

>>>>

directory <- here("data", "osf", "production", "trial-lists")
list_of_files = dir(here("data", "osf", "production", "trial-lists"))

@@

#
# JVC: ORIGINAL MODEL (singular fit)
#
intensity_model_lmer <- lmer(
  Intensity ~ typ_mean + 
    (1|target_name) + 
    (1|filename) + 
    (1|filename:target_name), 
  data = intensity_DF
  )
